New lower bounds for Schur and weak Schur numbers

### 2021-04-18 article/schur.tex
Suppression de quelques environnements remarque

\begin{remark}
	Here \(n\) is the "special" color: it has less constraints than the other colors. However, please note that \(n\) 
	is not necessarily the last color by order of appearance.
\end{remark}

\begin{remark}
	\(SF\)-templates include Abbott and Hanson's construction \cite{AbbottHanson} as a special case.
\end{remark}

@@

\begin{remark}
This proposition corresponds to the fact that sometimes a column is not the sum of two columns of a given color, but adding this 
column to the color would create sums in the color when applying the extension procedure. However, the last line does not 
intereact will all the columns when it comes to creating new sums. As a result, the hypotheses made on the colouring of the last 
row can be weakened.
\end{remark}

>>>>

Here \(n\) is the "special" color: it has less constraints than the other colors. However, please note that \(n\) 
is not necessarily the last color by order of appearance. \(SF\)-templates include Abbott and Hanson's construction \cite{AbbottHanson}
as a special case.

@@

This proposition corresponds to the fact that sometimes a column is not the sum of two columns of a given color, but adding this 
column to the color would create sums in the color when applying the extension procedure. However, the last line does not 
intereact will all the columns when it comes to creating new sums. As a result, the hypotheses made on the colouring of the last 
row can be weakened.
